\chapter*{Abstract}
\markboth{Abstract}{Abstract}
\thispagestyle{scrheadings}
\addcontentsline{toc}{chapter}{Abstract}

Classic \gls{gls-SIP} telephone systems enable real-time communication, but they do not offer intelligent speech processing. This thesis examines the technical feasibility of integrating large language models into container-based \gls{gls-SIP} telephone systems. The central research question is: Under what conditions do container-based approaches enable a stable connection between \gls{gls-SIP}-based telephony and \gls{gls-AI} speech models?

The prototype connects three core components: Asterisk handles \gls{gls-SIP} signaling, LiveKit processes \gls{gls-WebRTC} media streams, and a Python agent controls the \gls{gls-AI} logic. Speech processing is handled by OpenAI Whisper for speech recognition, GPT-4o-mini for dialogue management, and OpenAI Text-to-Speech for speech synthesis. The Docker-based implementation guarantees reproducibility. Iterative development began with a lightweight \gls{gls-SIP} agent called baresip to evaluate basic \gls{gls-SIP} mechanisms and gradually led to the final architecture.

The evaluation focuses on \gls{gls-SIP} integration. Five representative test calls were evaluated in detail. The median latency is 0.78 s for speech recognition and 1.41 s for speech synthesis. The system shows stable bidirectional audio transmission without timeouts. One \gls{gls-STT} misinterpretation was documented. \gls{gls-CPU} utilization is 11.2\%, and \gls{gls-RAM} requirements are between 11.2 and 12.1 GB. Audio quality achieves \gls{gls-MOS} values of 4.0 to 4.5.

The paper presents an \gls{gls-ETSI}-compliant architecture, demonstrates a functional implementation, provides evaluation data from \gls{gls-SIP} tests, and formulates recommendations for action for small and medium-sized enterprises. Open source solutions enable data protection-compliant deployments without vendor lock-in. The results show that \gls{gls-AI} language models can be combined with standard \gls{gls-VoIP} systems without specialized hardware to enable dialogue-oriented speech processing.

\noindent\textbf{Keywords:} Large Language Model, \gls{gls-SIP}, telephony, Docker-based architecture, Asterisk, LiveKit, \gls{gls-AI} integration
